Fixing Vulnerabilities Potentially Hinders Maintainability

### 2020-05-29 paper/icsme20.tex
fixes

\begin{abstract}
Security is a requirement of utmost importance to produce high-quality software. 
However, there is still a considerable amount of 
vulnerabilities being discovered and fixed, almost weekly. We suspect that developers 
affect the maintainability of their codebases when patching vulnerabilities. This paper evaluates the 
impact of patches to improve security on the maintainability of open-source 
software. Maintainability is measured based on the Better Code Hub’s model of 10 
guidelines using a dataset including 1335 security-related commits.
Results show evidence of a trade-off between security and maintainability, i.e., 
developers may be hindering software maintainability and introducing 
new vulnerabilities while patching vulnerabilities.
The implications of our study are that changes to codebases while patching 
vulnerabilities need to be performed with extra care (e.g., using tools
for patch risk assessment), computer science
curricula needs to be updated and more secure programming languages are necessary.
\end{abstract}
\begin{IEEEkeywords}
Security, Software Maintenance, Open-Source Software
\end{IEEEkeywords}

>>>>

\begin{abstract}
Security is a requirement of utmost importance to produce high-quality software. 
However, there is still a considerable amount of 
vulnerabilities being discovered and fixed, almost weekly. We suspect that developers 
affect the maintainability of their codebases when patching vulnerabilities. This paper evaluates the 
impact of patches to improve security on the maintainability of open-source 
software. Maintainability is measured based on the Better Code Hub’s model of 10 
guidelines using a dataset including 1335 security-related commits.
Results show evidence of a trade-off between security and maintainability, i.e., 
developers may be hindering software maintainability.
The implications 
of our study are that changes to codebases while patching 
vulnerabilities need to be performed with extra care; tools
for patch risk assessment should be integrate into the CI/CD pipeline; computer science
curricula needs to be updated; and, more secure programming languages are necessary.
\end{abstract}
\begin{IEEEkeywords}
Security, Software Maintenance, Open-Source Software
\end{IEEEkeywords}
